Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-12-21 ijar-npb-ms.tex
work on toy example

***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},
function \texttt{nonParBayesSystemInferencePriorSets()};
the package also contains the function \texttt{computeSystemSurvivalSignature()}
to calculate the survival signature for a given system layout (reliability block diagramm)***

>>>>

%***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},
The method is implemented in the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}
with the function \texttt{nonParBayesSystemInferencePriorSets()};
the package also contains the function \texttt{computeSystemSurvivalSignature()}
to calculate the survival signature for a given system layout (reliability block diagramm).

\begin{figure}
\centering
\begin{tikzpicture}
[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
%\begin{scope}[scale=0.75]
\node[type1] (T1)   at ( 0  , 0) {T1};
\node[type2] (T2)   at ( 2.8, 0) {T2};
\node[type3] (T3-2) at ( 1.4, 1) {T3};
\node[type3] (T3-3) at ( 1.4,-1) {T3};
\node[type3] (T3-5) at ( 4.2, 1) {T3};
\node[type3] (T3-6) at ( 4.2,-1) {T3};
\coordinate (start) at (-1,0);
\coordinate (end)   at (5.6,0);
\coordinate (bista) at (0.7,0);
\coordinate (biend) at (4.9,0);
\path (start)     edge[thick]   (T1.west)
      (T1.east)   edge[thick]   (bista)
      (bista)     edge[vh path] (T3-2.west)
                  edge[vh path] (T3-3.west)
      (T3-2.east) edge[hv path] (T2.north)
      (T3-3.east) edge[hv path] (T2.south)
      (T2.north)  edge[vh path] (T3-5.west)
      (T2.south)  edge[vh path] (T3-6.west)
      (T3-5.east) edge[hv path] (biend)
      (T3-6.east) edge[hv path] (biend)
      (biend)     edge[thick]   (end);
%\end{scope}
\end{tikzpicture}
\caption{Reliability block diagram for a `bridge' system with three component types.}
\label{fig:bridge-layout}
\end{figure}

As a toy example, consider a `bridge' type system layout with three types of components T1, T2 and T3,
as depicted in Figure~\ref{fig:bridge-layout}.
For components type T1 and T2, we consider a near-noninformative set of prior reliability functions.
For components of type T3, we consider an informative set of prior reliability functions
as given in Table~\ref{tab:bridge-T3prior}.
This set could result from eliciting prior functioning probabilities at times $0,1,2,3,4,5$ only,
and filling up the rest.
These prior assumptions, together with sets of posterior reliability functions
resulting from three different scenarios for test data for component type T3,
are illustrated in Figures~\ref{fig:bridge-fitting}, \ref{fig:bridge-early} and \ref{fig:bridge-late}; 
test data for components of type T1 and T2 are invariably
$\vec{t}^1 = (2.0, 2.2, 2.4, 2.6)$ and $\vec{t}^2 = (3.0, 3.2, 3.4, 3.6)$, respectively.

\begin{table}
\centering
\begin{tabular}{c|rrrrr}
$t$ & $[0,1)$ & $[1,2)$ & $[2,3)$ & $[3,4)$ & $[4,5)$ \\
\hline
$\ytzl{3}$ & 0.625 & 0.375 & 0.250 & 0.125 & 0.010 \\
$\ytzu{3}$ & 0.999 & 0.875 & 0.500 & 0.375 & 0.250
\end{tabular}
\caption{Lower and upper prior functioning probability bounds for component type T3 in the `bridge' system.}
\label{tab:bridge-T3prior}
\end{table}

In Figure~\ref{fig:bridge-fitting}, 
test data for component type T3 is $\vec{t}^3 = (0.5, 1.5, 2.5, 3.5)$,
and so in line with expectations.
The posterior set of reliability functions for each component type and the whole system
is considerably smaller as compared to the prior set
(due to the low prior strength intervals
$[\ntzl{1},\ntzu{1}] = [\ntzl{2},\ntzu{2}] = [1,2]$, $[\ntzl{3},\ntzu{3}] = [1,4]$)
and so giving more precise reliability statements.
We see that posterior lower and upper functioning probabilities drop at those times $t$
when there is a failure time in the test data,
or a drop in the prior functioning probability bounds.
Note that the lower bound for prior system reliability function is zero
due to the prior lower bound for T1;
for the system to function, the component of type T1 must function.

\begin{figure}
\includegraphics[width=\textwidth]{bridge-fittingfailures}
\caption{Prior and posterior sets of reliability functions for the `bridge' system and its three component types,
with failure times as expected for component type T3.
Test data failure times are denoted with tick marks near the time axis.}
\label{fig:bridge-fitting}
\end{figure}

In Figure~\ref{fig:bridge-early},
test data of component type T3 is instead $\vec{t}^3 = (0.6, 0.7, 0.8, 0.9)$,
and so earlier than expected.

\begin{figure}
\includegraphics[width=\textwidth]{bridge-earlyfailures}
\caption{Prior and posterior sets of reliability functions for the `bridge' type system and its three component types,
with failure times earlier as expected for component type T3.}
\label{fig:bridge-early}
\end{figure}

In Figure~\ref{fig:bridge-late}, 
test data of component type T3 is now $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
and so later than expected.

\begin{figure}
\includegraphics[width=\textwidth]{bridge-latefailures}
\caption{Prior and posterior sets of reliability functions for the `bridge' type system and its three component types,
with failure times later as expected for component type T3.}
\label{fig:bridge-late}
\end{figure}
